Introduction to Robot Operating System (ROS)

### 2019-05-31 presentationNotes.tex
comment

\begin{document}
%
% paper title
% can use linebreaks \\ within to get better formatting as desired
%\title{Time Varying Operator for Controlling Nonholonomic Systems with Drift}
\title{Universal Control Law for Nonholonomic Systems with Drift}

\author{Md Suruz~Miah,~\IEEEmembership{Senior Member,~IEEE}% and 
%		N.~U.~Ahmed                
\thanks{S.~Miah is with the Electrical and Computer Engineering Department, Bradley University, Peoria, IL, 61625, USA. e-Mails:~smiah@bradley.edu}% <-this % stops a space
%\thanks{S.~Miah is with the Electrical and Computer Engineering Department, Bradley University, Peoria, IL, 61625, USA. e-Mail:~smiah@bradley.edu}% <-this % stops a space

@@

\thanks{This research supported in part by Caterpillar Inc.}
}
% The paper headers
%\markboth{Journal of \LaTeX\ Class Files,~Vol.~6, No.~1, January~2007}%

@@

\begin{abstract}
A universal control law for nonholonomic systems with drift is considered. While the development of feedback control laws for controlling nonlinear dynamical systems are well-established in the literature to date, the need of a control theoretic method to establish a universal control law for a class of nonlinear systems is significant. 
This is simply because the formulation of feedback control laws  relies on types of dynamical systems to be controlled which lead to a significant technical challenge for researchers.% to propose a general feedback law for a class of  nonlinear dynamical systems. %This task is even more challenging when the system is only partially observable. 
%
Here we underscore the need for a universal control law  that is aimed to address the trajectory tracking problem of nonholonomic systems with drift. For that, we propose to develop a time-varying feedback operator (called  herein a universal control law), to solve the tracking problem. The objective of the current manuscript is to prove the existence and to establish necessary conditions of the proposed time-varying feedback operator for nonholonomic systems with drift. The performance of the time-varying feedback operator will be backed up by a set of computer simulations. The novelty of this research lies in the modularity of the control law despite inherent non-linearity of nonholonoic systems. 
%
%complex dynamical systems.%, such as differential drive mobile robots, underwater or flying vehicles, and  competitive systems (\textit{e.g.,} mixing of renewable and nonrenewable energy sources).

\end{abstract}

% Note that keywords are not normally used for peerreview papers.
\begin{IEEEkeywords}
Generalized control law, nonholonomic systems, drift, Pontryagin's minimum principle.
\end{IEEEkeywords}
\IEEEpeerreviewmaketitle

%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}

\section{Notations and Preliminaries}\label{sec:notations}
Throughout this paper, scalar and vector quantities will be denoted by non-bold letters and lower-case bold letters, respectively. Upper-case bold letters will denote matrices. For any positive integer $n$, $\mathbb{R}^n$ denotes the Euclidean space. For any vector ${\bf x,y}\in\mathbb{R}^n$, the standard Euclidean norm and the scalar product are given by
\begin{equation*}
\|{\bf x}\| \equiv  \left[\sum_{i=1}^n \left |x_i\right |^2\right]^{1/2}~\hbox{and}~~ {\bf (x\cdot y)}\equiv{\bf x}^T{\bf y}\equiv\sum_{i=1}^n x_i y_i, 
\end{equation*}
respectively. We shall use $\mathbb{R}^{m\times n}$ to denote the space of $m\times n$ matrices with entries from $\mathbb{R}$.  Let ${\bf X,Y}\in\mathbb{R}^{m\times n}$, then the standard norm and their scalar product are also given by 
\begin{equation*}
\begin{split}
\|{\bf X}\|\equiv\left[\sum_{i=1}^m \sum_{j=1}^n\left |x_{i,j}\right |^2\right]^{1/2}~\text{and}~{\bf (X\cdot Y)}\equiv Tr\left[{\bf X}^T{\bf Y}\right]\equiv Tr\left[{\bf X}{\bf Y}^T\right],
\end{split}
\end{equation*}
respectively, where $\mathrm{Tr}\left[\cdot\right]$ denotes the trace of matrix $\left[\cdot\right]$. Clearly, $\mathrm{Tr}\left[{\bf X}^T{\bf X}\right]=\|{\bf X}\|^2$. ${\bf X}\otimes {\bf Y}$ is the Kronecker product of two matrices ${\bf X,Y},$ where $\mathbb{R}^{m^2\times n^2}\ni {\bf Z} = {\bf X}\otimes {\bf Y}.$ $C({\cal I}, \mathbb{R}^n)$ is the class of all continuous function on the time interval ${\cal I}$ taking values from~$\mathbb{R}^n.$

If the function $J:\mathbb{R}^n\to \mathbb{R}$ is differentiable at ${\bf x}\in \mathbb{R}^n$, then for any ${\bf v}\in\mathbb{R}^n$, $dJ({\bf x};{\bf v})$ denotes the Gateaux (directional) derivative in the direction of ${\bf v}$, which is given by
%
\begin{equation*}
dJ({\bf x};{\bf v}) = {\bf v}^T\nabla J=\lim_{\varepsilon\to 0} \frac{J({\bf x} + \varepsilon{\bf v}) - J({\bf x})}{\varepsilon}, 
\end{equation*}
where $\nabla J$ denotes the gradient of $J$.
%
However, if $J:\mathbb{R}^{m\times n}\to \mathbb{R}$, then for any ${\bf X},{\bf V}\in\mathbb{R}^{m\times n}$, the directional derivative in the direction of ${\bf V}$ is defined by
\begin{equation*}
dJ({\bf X};{\bf V}) = Tr[{\bf V}^T\nabla J] = \lim_{\varepsilon\to 0} \frac{J({\bf X} + \varepsilon{\bf V}) - J({\bf X})}{\varepsilon}. 
\end{equation*}
For any bounded time interval ${\cal I} \equiv [0, t_f],~t_f>0,$ $C({\cal I},\mathbb{R}^n)$ denotes the class of all continuous functions on ${\cal I}$ taking values in $\mathbb{R}^n$. Let $p \in [1,\infty)$ and  any finite time interval ${\cal I}$, we use  ${\cal L}_p({\cal I},\mathbb{R}^n)$ to denote the set of Lebesgue measurable functions $\{{\bf f}\}$ defined on ${\cal I}$ and taking values in $\mathbb{R}^n$ whose norms are $p$-th power integrable,~\textit{i.e.,}~
%\begin{equation*}
$L_p({\bf f}) = \left(\int_{0}^{t_f}\|{\bf f}\|^p \mathrm{dt}\right)^{1/p}<\infty,$ 
%\end{equation*}
%
where $L_p({\bf f})$ denotes the $p$th norm of the function ${\bf f}$~\cite{Royden2010,Khalil2002}. For $p=\infty$, ${\cal L}_{\infty}({\cal I},R^n)$ denotes the space  of Lebesgue measurable functions $\{{\bf f}\}$ defined on ${\cal I}$ and taking values in $\mathbb{R}^n$ satisfying 
%
%\begin{equation*}
$\text{ess sup} \{ \|{\bf f}(t)\|, t \in {\cal I}\} < \infty.$
%\end{equation*}
%
% Similarly, ${\cal L}_p^{\ell oc}([0,\infty),\mathbb{R}^n)$ are locally convex topological vector spaces of $p$-th power locally integrable functions containing the  spaces ${\cal L}_p(I,\mathbb{R}^n)$.
%We use $\mathrm{diag}(a_1,\ldots,a_n)$ to represent a matrix whose diagonal entries starting in the upper left corner are $a_1,\ldots,a_n$.

\section{System Model and Problem Statement}
\label{sec:systemModel}
\subsection{System Model}
We consider a class of dynamical systems described by 
\begin{subequations}
\label{eq:system}
\begin{align}
\label{eq:systemModel}
\dot{{\bf q}}(t) & = \bar{{\bf g}}({\bf q}(t)) + \sum_{j=1}^m{\bf g}_j({\bf q}(t))u_j(t),\\
\label{eq:controlLaw}
u_j(t) & = {\bf k}_j^T(t) {\bf q}(t), 
\end{align}
\end{subequations}
where ${\bf q}(t)\in{\cal Q}\subset\mathbb{R}^n$ is the state of the system at time $t\ge 0$ with ${\cal Q}$ being its state space, $u_j$ is the $j$th, $j=1,\ldots, m$ control variable, and ${\bf k}_j: \mathbb{R}\to \mathbb{R}^n$ is the time-varying feedback operator of the $j$th control variable for positive integer $n,$ $m$ with $n>m$. The drift vector field $\bar{{\bf g}}:\mathbb{R}^n\to\mathbb{R}^n$ represents natural unforced motion of the system and ${\bf g}_j:\mathbb{R}^n\to\mathbb{R}^n,$ $j=1,\ldots,m,$ are linearly independent control vector fields~\cite{Choset2004}. When no ambiguity arises, we shall drop the argument $(t)$ for clarity. System~\eqref{eq:system} can also be written in compact form as
%
\begin{subequations}
\label{eq:system1}
\begin{align}
\label{eq:systemModel1}
\dot{{\bf q}} & = \bar{{\bf g}}({\bf q}) + {\bf G}({\bf q}){\bf u},\\
\label{eq:controlLaw1}
{\bf u} & = {\bf K}(t) {\bf q}, 
\end{align}
\end{subequations}
%
where ${\bf u}\in{\cal U}\subset \mathbb{R}^m$ is the vector of $m$ control inputs to the system, ${\bf G}:\mathbb{R}^n\to\mathbb{R}^{n\times m},$ and the time varying feedback operator ${\bf K}:\mathbb{R}_0^+\to{\cal K}_{\mathrm{ad}}\subset\mathbb{R}^{m\times n}.$

Note the difference in the feedback control law in~\eqref{eq:controlLaw1} with other existing control laws in the literature. It is simply a matter of determining the universal matrix (herein called feedback operator) ${\bf K}(t)\in{\cal K}\subset\mathbb{R}^{m\times n}.$

\subsection{Problem Formulation} 
Let ${\bf q}^d(t)$ be the desired (reference) trajectory that the system~\eqref{eq:systemModel1} is supposed to track and $e(t) = \|{\bf q}(t)-{\bf q}^d(t)\|_{\mathbb{R}^n}$ denotes its state tracking error, for $t\in {\cal I}$. The objective is to find the optimal time-varying feedback operator  ${\bf K}(t)\in {\cal K}_{ad}$ that generates the trajectory ${\bf q}(t)\in{\cal Q}$ while minimizing the average cumulative state tracking error, $\mathscr{E}_{\mathrm{avg}}$, given by 
\begin{equation}
\mathscr{E}_{\mathrm{avg}} = \frac{1}{t_f}\int_{0}^{t_f}e(t)\mathrm{dt},~~t_f>0.
\label{eq:tracking-error}
\end{equation}

Given the system model~\eqref{eq:system1}, the problem can be stated as follows:
\begin{equation}
\inf_{\{{\bf q}\in{\cal Q},~{\bf K}\in{\cal K}_{ad}\}} [\mathscr{E}_{\mathrm{avg}}].
\label{eq:problem}
\end{equation}

\section{Proposed Universal Control Law}
\label{sec:feedbackOperator}
This section details the design procedure of the proposed universal time-varying control law, which is the main contribution of this manuscript. Substituting~\eqref{eq:controlLaw1} in~\eqref{eq:systemModel1}, yields the following full-state feedback system:
\begin{equation}
\begin{split}
\dot{{\bf q}}  = \bar{{\bf g}}({\bf q}) + {\bf G}({\bf q}){\bf K}(t) {\bf q} \equiv{\bf f}({\bf q},{\bf K}),
\end{split}
\label{eq:systemFeedbackFull}
\end{equation}
with ${\bf q}(0)={\bf q}_0.$ We emphasize that the generalized linear time varying operator ${\bf K}(t)$ completely characterizes the feedback law~\eqref{eq:systemFeedbackFull} for solving the trajectory tracking problem.

\begin{lemma}[Solutions of feedback system]
\label{lem:feedback-sol}
Given the feedback system~\eqref{eq:systemFeedbackFull}, which is defined over the finite time horizon of ${\cal I}$, then for every initial condition ${\bf q}(0)\in\mathbb{R}^n$, and feedback operator ${\bf K}(t)\in {\cal K}_{ad}$, the system~\eqref{eq:systemFeedbackFull} has a unique absolutely continuous solution ${\bf q}(t)\in C({\cal I}, \mathbb{R}^n)$. Furthermore, the solution set ${\cal Q}\equiv\left\{{\bf q}(t) \equiv{\bf q}[t,{\bf K}(t)]\in C({\cal I},\mathbb{R}^n):{\bf K}(t)\in {\cal K}_{ad}\right \}$ is a bounded subset of $C({\cal I}, \mathbb{R}^n)$. 
\end{lemma}
%\begin{IEEEproof}
The proof of this lemma is classical and follows from a similar technique in~\cite[page~89]{Ahmed2006}. %
%\end{IEEEproof}
Hence, the actual trajectory of the of the vehicle can then be symbolically represented by 
\begin{equation}
{\bf q}(t) = {\bf q}(0) + \int_{0}^{t}{\bf f}[{\bf q}(\tau),{\bf K}(\tau)]d\tau,
\label{eq:actual-trajectory-full} 
\end{equation}
for $t\in {\cal I}$. In order to solve the trajectory tracking problem of nonholonomic systems with drift, let us introduce the cost functional as
\begin{equation}
J({\bf K}) = \Phi [t_f,{\bf q}(t_f)] + \int_{0}^{t_f} \ell [t,{\bf q}(t,{\bf K})]\mathrm{dt},~~\mathrm{with}
\label{eq:cost-fn}
\end{equation}
\begin{multline*}
\Phi [t_f,{\bf q}(t_f)]= \frac{1}{2} [{\bf q}(t_f)-{\bf q}^d(t_f)]^T{\bf P}(t_f)[{\bf q}(t_f)-{\bf q}^d(t_f)] ~\mathrm{and}~\\
\ell [t,{\bf q}(t)] =\frac{1}{2}[{\bf q}(t)-{\bf q}^d(t)]^T{\bf Q}(t)[{\bf q}(t)-{\bf q}^d(t)],
%\label{eq:cost-fn}
\end{multline*}
where the weight matrix ${\bf P}(t_f) \in\mathbb{R}^{n\times n}$ and the  tracking weight ${\bf Q}(t)\in\mathbb{R}^{n\times n}$ are symmetric positive definite matrices that indicate the relative importance of the error components along $\mathbb{R}^n.$ %
%
%If the vehicle's purpose is to stabilize on a fixed configuration, then ${\bf P}(t_f)$ must be higher than ${\bf Q}(t)$ and the desired trajectory is set to a \emph{fixed} configuration. However, the opposite is true for the vehicle to track a desired trajectory. 
%
The performance index $J({\bf K})$ in~\eqref{eq:cost-fn} depends on the feedback operator ${\bf K}(t)$ through the state variable ${\bf q}(t)$ as it is clear from the feedback system~\eqref{eq:systemFeedbackFull}. Note that $\Phi[\cdot]$ and $\ell[\cdot]$ of~\eqref{eq:cost-fn} are referred to as the terminal and tracking cost functionals, respectively. The task now becomes solving the following problem:
\begin{equation}
\inf_{{\bf K}\in{\cal K}_{ad}} [J({\bf K})],
\label{eq:problem1}
\end{equation}
which yields ${\bf q}(t) \to {\bf q}^d(t)$ as $J({\bf K})\longrightarrow 0$, for $t\in {\cal I}$. It is important to point out that, solving the problem~\eqref{eq:problem1} will eventually solve  the problem~\eqref{eq:problem}. Hence, the problem~\eqref{eq:problem1} can be solved if there exists a generalized optimal feedback operator ${\bf K}^*(t)$, for $t\in {\cal I}.$ However, it is worth noting the following remark before we proceed determining the generalized control law ${\bf K}(t).$ 
%

\begin{remark}
Note that the optimal feedback gain ${\bf K}(t)$ can be determined by following the classical Pontryagin's minimum principle~\cite[Chaper~8]{Ahmed2006} with ${\bf K}(t)$ being the open--loop control input to the feedback system~\eqref{eq:systemFeedbackFull}. For that, let $\mathrm{vec}({\bf K}(t))$ transforms the matrix ${\bf K}(t)$ into a column vector, which is formed by stacking the rows of ${\bf K}(t).$ The feedback model~\eqref{eq:systemFeedbackFull} can be rewritten as 
\begin{equation}
  {\bf \dot q} = \bar{{\bf g}}({\bf q}) + \left({\bf q}^T\otimes{\bf G}({\bf q})\right){\bf \bar k},
  \label{eq:systemFeedbackFull1}  
\end{equation}
where $\mathbb{R}^{nm}\ni{\bf \bar k}=\mathrm{vec}({\bf K})$ is now the control input vector that can be solved by following the standard gradient descent technique presented in~\cite[Chapter~3]{Stengel1994}~\cite[Chaper~8]{Ahmed2006}. By rearranging the elements of the optimal vector ${\bf \bar k}^*,$ we can reconstruct the optimal feedback operator ${\bf K}^*$ which is then substituted in the feedback law~\eqref{eq:systemFeedbackFull} to generate the optimal control input vector ${\bf u}^*(t),$ for $t\in{\cal I}.$  Nevertheless,  we emphasize in determining the optimal feedback operator ${\bf K}^*(t)$ directly by modifying the classical Pontryagin's minimum principle, which has applications in solving problems of a general class of partially observed dynamic systems. 
\end{remark}

\subsection{Existence of Generalized Control Law}
In this section, we provide the proof of the existence of the proposed generalized time-varying control law, ${\bf K}(t),$ that essentially solves the tracking problems of nonholonomic systems with drift.

\begin{theorem}\label{thm:existence-K}
Given a nonholonomic system modeled by \eqref{eq:systemModel1}, there exists a generalized optimal control law ${\bf K}^*(t) \in {\cal K}_{ad}$ for the controller modeled in~\eqref{eq:controlLaw1} that drives the system~\eqref{eq:systemModel1} to the desired trajectory ${\bf q}^d(t)$ while finding the optimal solution for the problem~\eqref{eq:problem}. 
\end{theorem}
%%See Appendix~\ref{app:thm:existence-K} for its complete proof. %
 \begin{proof} 
Following the well known Alaoglu's theorem\footnote{\href{https://en.wikipedia.org/wiki/Banach/wiki/Banach–Alaoglu_theorem}{https://en.wikipedia.org/wiki/Banach/wiki/Banach–Alaoglu\_theorem}},  ${\cal K}_{ad} \subset {\cal K}\subset\mathbb{R}^{m\times n}$  is a (weak star) $w^*$ compact set and it suffices to prove that ${\bf K} \longmapsto J({\bf K})$ is sequentially weak star continuous. Let $\{{\bf K}^i, i \in \mathbb{N}\} \in {\cal K}_{ad}$ be a sequence  and suppose   ${\bf K}^i \buildrel w^* \over \to {\bf K}^*.$ Since ${\cal K}_{ad}$ is $w^*$ closed,  we have ${\bf K}^* \in {\cal K}_{ad}$, see~\cite{AhMi2011-j1}.

Suppressing the variable $t$ for clarity, let $\{{\bf q}^i,~i\in \mathbb{N}\}$ and ${\bf q}^*$ denote the  solutions of the system~\eqref{eq:systemFeedbackFull} corresponding to $\{{\bf K}^i,~i\in \mathbb{N}\}$ and ${\bf K}^*$, respectively. Hence, the corresponding state equation becomes 
\begin{align*}
{\bf \dot q}^i = {\bf f}({\bf q}^i,{\bf K}^i)~\text{and}~
{\bf \dot q}^* = {\bf f}({\bf q}^*,{\bf K}^*),~{\bf q}^i_0={\bf q}^*_0={\bf q}_0.
\end{align*}
%
Using~\eqref{eq:actual-trajectory-full}, the solutions of the above two state-space models can be described by
\begin{equation*}
\begin{split}
{\bf q}^i(t) = {\bf q}_0 + \int_{0}^{t}{\bf f}[{\bf q}^i(\tau),{\bf K}^i(\tau)]d\tau,~\text{and}~~
{\bf q}^*(t)= {\bf q}_0 + \int_{0}^{t}{\bf f}[{\bf q}^*(\tau),{\bf K}^*(\tau)]d\tau.
\end{split}
\end{equation*}
%
Subtracting one from another, we get
\begin{align}
{\bf q}^i(t)-{\bf q}^*(t) = \int_{0}^t\left({\bf f}[{\bf q}^i(\tau),{\bf K}^i(\tau)]- {\bf f}[{\bf q}^*(\tau),{\bf K}^*(\tau)]\right)d\tau.
\label{eq:existence-temp1}
\end{align}
Note that ${\bf G}({\bf q}^i),~i\in \mathbb{N}$ and ${\bf G}({\bf q}^*)$ are uniformly bounded functions and satisfy Lipschitz condition
\begin{align*}
\|{\bf G}({\bf q}^i)-{\bf G}({\bf q}^*)\|&\leq L_{c2}\|{\bf q}^i-{\bf q}^*\|,\\
\|\bar{{\bf g}}({\bf q}^i)-\bar{{\bf g}}({\bf q}^*)\|&\leq L_{c1}\|{\bf q}^i-{\bf q}^*\|,\\
\end{align*}
where $L_{c1}$ and $L_{c2}$ are Lipschitz constants. Taking the Euclidean norm in both sides of expression~\eqref{eq:existence-temp1} and using the triangle inequality yield
\begin{align*}
\|{\bf q}^i(t)-{\bf q}^*(t)\| \leq v^i(t)+\int_{0}^t\beta(\tau)\|{\bf q}^i(\tau)-{\bf q}^*(\tau)\|d\tau,~\text{where}
\end{align*}
%
\begin{equation*}
v^i(t) = \Big\Vert\int_{0}^t\left[{\bf G}({\bf q}^i)({\bf K}^i-{\bf K}^*){\bf q}^i\right]d\tau\Big\Vert,
\end{equation*}
${\beta}(t) = (L_{c1} + c_1(t) + c_2(t)L_{c2}) \in{\cal L}_1^{+}({\cal I})$, with 
\begin{align*}
c_1(t)=[\sup \|{\bf G}({\bf q}^i)\|][\sup \|{\bf K}\|],~c_2(t) = \sup(\|{\bf K}^*\|\|{\bf q}\|),
\end{align*}
for $i\in \mathbb{N},~{\bf K}\in{\cal K},~\text{and}~{\bf q}\in{\cal Q}$ (see Theorem 8.3.4 of~\cite[page 273]{Ahmed2006} for more details). Thus,  it follows from Gronwall inequality that 
\begin{equation} 
\parallel {\bf q}^i(t) - {\bf q}^*(t)\parallel \leq v^i(t) + 
\int_{0}^t \exp\{\int_{\tau}^t \beta(s)\mathrm{ds}\} \beta(\tau) v^i(\tau) d\tau.
\label{eq:gronwall}
\end{equation} 
Clearly, $v^i(t)\to 0$, for $t\in {\cal I}$, $i\in \mathbb{N}$, as ${\bf K}^i\buildrel w^* \over \to {\bf K}^*$. Thus, it follows from inequality~\eqref{eq:gronwall} that ${\bf q}^i\buildrel {\bf K}^*\over \to {\bf q}^*.$ 
%
Since both $\ell (t,\cdot)$ and $\Phi(t,\cdot)$ are continuous on $\mathbb{R}^n,$ we have  $\ell[t,{\bf q}_i(t)] \longrightarrow \ell[t,{\bf q}^*(t)] $ for almost all $t \in {\cal I}$ and $\Phi[t,{\bf q}^i(t_f)] \longrightarrow \Phi[t,{\bf q}^*(t_f)] $ as $i \rightarrow \infty.$ Thus it follows from the expression \eqref{eq:cost-fn} that  $ \lim_{i \rightarrow \infty} J({\bf K}^i)  =  J({\bf K}^*)$ proving weak star continuity of  $J$ on ${\cal K}_{ad}.$ Since ${\cal K}_{ad}$ weak  star compact, $J$  attains its minimum on ${\cal K}_{ad}.$ 
\end{proof}
% 
Theorem~\ref{thm:existence-K} guarantees that there exists an optimal universal control law ${\bf K}^*$ for nonholonomic systems modeled by~\eqref{eq:systemModel}. In the following, we provide the necessary conditions for the proposed universal control law.

\subsection{Necessary Conditions}
\label{sec:necessaryConditions}

To solve for the optimal trajectory that minimizes the objective functional~\eqref{eq:cost-fn}, we need to derive the necessary conditions of optimality. These necessary conditions are most readily found if the integrand of the cost functional~\eqref{eq:cost-fn} is recast in terms of Hamiltonian 
%\begin{equation*}
$\mathcal{H}:{\cal I}\times \mathbb{R}^n\times\mathbb{R}^n\times\mathbb{R}^{m\times n} \longrightarrow \mathbb{R}$,
%\end{equation*}
which is expressed by
%
\begin{equation}
\mathcal{H}[t, {\bf q}(t), \boldsymbol{\psi}(t),{\bf K}(t)] = \boldsymbol{\psi}^T(t){\bf f}[{\bf q}(t),{\bf K}(t)] + \ell[t,{\bf q}(t)],
\label{eq:hamiltonian}
\end{equation}
%
where $\boldsymbol{\psi}(t)\in\mathbb{R}^n,~t\in {\cal I}$, is a vector of Lagrange multipliers whose elements are the co-states of the system~\cite{Ahmed1988}. We now derive the necessary conditions of optimality feedback model~\eqref{eq:systemFeedbackFull}.

\begin{theorem}
\label{thm:necessary-conditions}
Since the optimal universal feedback operator (control law) ${\bf K}^*(t),~t\in {\cal I}$ exists, the optimal trajectory ${\bf q}^*(t),~t\in {\cal I}$ for the feedback model~\eqref{eq:systemFeedbackFull} can be obtained if there exists an optimal multiplier $\boldsymbol{\psi}^*(t)\in C({\cal I},\mathbb{R}^n)$ such that the triple $\{{\bf q}^*,\boldsymbol{\psi}^*,{\bf K}^*\}$ satisfies the following necessary conditions:
\begin{subequations}
\begin{align}
\label{eq:inequality-H}
{\cal H}[t,{\bf q}^*(t),\boldsymbol{\psi}^*(t),{\bf K}(t)] & \geq{\cal H}[t,{\bf q^*}(t),\boldsymbol{\psi}^*(t),{\bf K^*}(t)], ~~{\bf K}(t)\in {\cal K},\\
\label{eq:state}
{\bf \dot q}^* &=\frac{\partial{\cal H}}{\partial\boldsymbol{\psi}} [t,{\bf q}^*(t),\boldsymbol{\psi}^*(t),{\bf K^*}(t)],~{\bf q}^*(0)={\bf q_0},\\
\label{eq:costate}
\boldsymbol{\dot\psi}^* &= -\frac{\partial{\cal H}}{\partial{\bf q}} [t,{\bf q}^*(t),\boldsymbol{\psi}^*(t),{\bf K}^*(t),~\boldsymbol{\psi}^*(t_f) = \frac{\partial\Phi}{\partial{\bf q}}[t_f,{\bf q}(t_f)].
\end{align}
\end{subequations}
\end{theorem}
%% The detailed and comprehensive proof of this Theorem is given in Appendix~\ref{app:thm:necessary-conditions}. %
\begin{proof}
Let ${\bf q}(t)\equiv{\bf q}[t,{\bf K}(t)]$ be the solution of the feedback system~\eqref{eq:systemFeedbackFull}, with the cost functional~\eqref{eq:cost-fn} for any choice of ${\bf K}(t)\in{\cal K}_{ad}$. Since ${\bf K}^*(t)$ is optimal with the associated trajectory ${\bf q}^*(t)$, it is clear that
\begin{equation*}
J({\bf K}^*) \leq J({\bf K}),~~\forall~{\bf K}(t)\in{\cal K}_{ad},~t\in {\cal I}. 
\end{equation*}
Suppressing the variable $t$ for clarity and for any $\varepsilon\in [0,1]$, we define ${\bf K}^{\varepsilon}={\bf K}^* + \varepsilon ({\bf K-K^*})$. Since ${\cal K}$ is a closed convex set, ${\cal K}_{ad}$ is also a closed convex subset of ${\cal L}_{\infty}({\cal I},\mathbb{R}^{m\times n})$ and therefore ${\bf K}^{\varepsilon}\in{\cal K}_{ad}$. Thus $J({\bf K^*}) \leq J({\bf K}^{\varepsilon})$, which follows that
\begin{equation}
dJ({\bf K}^*;{\bf K}-{\bf K}^*)=\mathrm{Tr}\left[\left({\bf K}-{\bf K}^*\right)^T\nabla J({\bf K}^*)\right]\geq 0,
\label{eq:dJ}
\end{equation}
where $dJ({\bf K}^*;{\bf K}-{\bf K}^*)$ denotes the Gateaux (directional) derivative of $J$ evaluated at ${\bf K}={\bf K}^*$ in the direction of $({\bf K}-{\bf K}^*)$ and $\nabla J({\bf K}^*)$ is the gradient of $J$ evaluated at ${\bf K}^*$.

>>>>

\begin{document}
%
% paper title
% can use linebreaks \\ within to get better formatting as desired
%\title{Time Varying Operator for Controlling Nonholonomic Systems with Drift}
\title{Introduction to Robot Operating System (ROS)}

\author{Amr Elhussein, Advisor: Dr. Suruz Miah %~\IEEEmembership{Senior Member,~IEEE}% and 
%		N.~U.~Ahmed                
%\thanks{S.~Miah is with the Electrical and Computer Engineering Department, Bradley University, Peoria, IL, 61625, USA. e-Mails:~smiah@bradley.edu}% <-this % stops a space
%\thanks{S.~Miah is with the Electrical and Computer Engineering Department, Bradley University, Peoria, IL, 61625, USA. e-Mail:~smiah@bradley.edu}% <-this % stops a space

@@

%\thanks{This research supported in part by Caterpillar Inc.}
}
% The paper headers
%\markboth{Journal of \LaTeX\ Class Files,~Vol.~6, No.~1, January~2007}%

@@

%\begin{abstract}
%A universal control law for nonholonomic systems with drift is considered. While the development of feedback control laws for controlling nonlinear dynamical systems are well-established in the literature to date, the need of a control theoretic method to establish a universal control law for a class of nonlinear systems is significant. 
%This is simply because the formulation of feedback control laws  relies on types of dynamical systems to be controlled which lead to a significant technical challenge for researchers.% to propose a general feedback law for a class of  nonlinear dynamical systems. %This task is even more challenging when the system is only partially observable. 
%
%Here we underscore the need for a universal control law  that is aimed to address the trajectory tracking problem of nonholonomic systems with drift. For that, we propose to develop a time-varying feedback operator (called  herein a universal control law), to solve the tracking problem. The objective of the current manuscript is to prove the existence and to establish necessary conditions of the proposed time-varying feedback operator for nonholonomic systems with drift. The performance of the time-varying feedback operator will be backed up by a set of computer simulations. The novelty of this research lies in the modularity of the control law despite inherent non-linearity of nonholonoic systems. 
%
%complex dynamical systems.%, such as differential drive mobile robots, underwater or flying vehicles, and  competitive systems (\textit{e.g.,} mixing of renewable and nonrenewable energy sources).

%\end{abstract}

% Note that keywords are not normally used for peerreview papers.
%\begin{IEEEkeywords}
%Generalized control law, nonholonomic systems, drift, Pontryagin's minimum principle.
%\end{IEEEkeywords}
%\IEEEpeerreviewmaketitle

%%%%%%%%%%%%%%%%%%%%%%
\section{Slide 1: Outine}
Hi every one my name is Amr Elhussein, mechanical enginering graduate student, i've been interested in working in robotics for four years now and i want to thank Dr. Miah to give me the chance to finally work in the field. 
In today's presentaion we will be talking about ROS, we will talk a litle bit about its origin, how was things done before ros, what ROS exactly is and some applications. 
We will also walk through major concepts in ROS, how to install it and an overview on the future of ROS.
\section{Slide 2: Historiccal Background}
ROS started in 2007 as an outgrowth of Stanford AI robot (STAIR) and lately sponsored by willow grage a robotics incubator. 
Ros is Currently extensively used in academia and industry. Currenlty ROS is supported by what is known as open source robotics foundation. 
\section{Slide 3: Robot programming before ROS}
Before ROS developing robots was very time consuming because there were no common platform for doing so. instead developers built every thing from scratch and implement algorithms on their own. 
\section{Slide 4: ROS is } 
A flexible framework for writing robot software. It is a collection of tools,
libraries, and conventions that aim to simplify the task of creating complex
and robust robot behavior across a wide variety of robotic platforms.
\section{Slide 5: ROS Equation}
To get more understanding of ROS, we can say that ROS is a combination of plumbing which are used to connect different parts of the robot, tools that are used in visualisation and other tasks one example of those tools is Gazebo which is a 3D visulisation tool used to simulate real world enviroments, Capabilities such as of the shelf algorithms that are ready to reuse and Ecosystem and community support which is an essential component of ROS.
\section{Slide 6: Applications}
As we mentioned earlier ROS is widely used in so many areas that includes : autonomus vehicles , warehouses and industrial applications. ROS also has been used to train robotics teams in First Robotics high school competion.
\section{Slide 7: ROS Concepts, File System }
When using ROS there are three levels of concepts one must deeply understand, the first level is the filesystem which consists of:
\\Packages: the atomic unit of ROS which contains executable and supporting files that serve a specific purpose. 
\\metapackages : which serves to represent a group pf related other packages.
